---
title: District report
params:
  area: Medway
---
  
```{r setup, echo=FALSE}

library(fingertipsR)

```

# `r params$area`  
Produced: `r Sys.Date()`

* In this version of the Rmd file we check to see if the data object `LEdata` exists and only try to get the data from the fingtertips website if it does not.
* It is important to use a unique object name for the data and to avoid modifying it. Instead create a separate trimmed-down version. This is so that you can use the original object again when you need to run the report for a different area, etc.


## Life expectancy

```{r lifeexpectany, echo=FALSE}

## If the LA_data object does not exist, download the data from
## the fingertips website
if (!exists("LEdata")) LEdata <- fingertips_data(90366, AreaTypeID = 101)

## We create a logical vector i that is true for rows where the area name is 
## the one we have selected and sex is male 
i <- LEdata$AreaName == params$area & LEdata$Sex == "Male" 
LEdata_m <- LEdata[i, ]

## We want to have the year of the most recent data point in the narrative so
## we find the maximum timeperiod. We use the sortable version to do this, but it
## does not look very nice, so we use it to identify the more readable version
## in the timeperiod column.
max_year <- max(LEdata_m$TimeperiodSortable)
max_year <- LEdata_m$Timeperiod[LEdata_m$TimeperiodSortable == max_year]
i <- LEdata_m$Timeperiod == max_year

## Use this logical vector to get the life expectancy value
LE_m <- LEdata_m$Value[i]
LE_m <- round(LE_m, 1)


```

Life expectancy in males in `r params$area` in `r max_year` was `r LE_m` years. 

